Response to the defense feedback

### 2021-06-03 Chapter-2/Chapter-2.tex
Updates from Overleaf

\subsubsection*{Machine Learning Applications}
Recent side-channel attacks on machine learning applications mainly focus on recovering two types of sensitive information: the input of the model and the architecture of deep learning models. Hua et al.~\cite{hua2018reverse} were the first in the literature to reverse engineer the architecture of convolutional neural networks (CNNs) through the memory access patterns. Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network by using the power consumption to recover inputs to the networks. For an image classification task trained by the MNIST dataset, their attacks can achieve up 89\% accuracy. CSI NN~\cite{batina2019csi} reverse engineered the multi-layer perception and convolution neural network based on the electromagnetic signals (EMs). Cache Telepathy~\cite{yan2020cache} introduces the cache-based side-channel attack to extract DNNs' architectures. We find that all existing approaches need a lot of domain knowledge and expertise to launch the attacks.
\subsubsection*{Media and Graphic Libraries}
Recent work also studies the side-channel attacks in media and graphic libraries. Gruss et at.~\cite{191010} show an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library. In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al. demonstrate an attack to recover the outline of an image by exploiting the vulnerability in the inverse DCT function in libjpeg. Daimeng et al.~\cite{wang2019unveiling} present a cache attack on graphic libraries. Their approaches uses a machine learning approach to pick cache lines that can be exploitable to leak the most information.
\subsubsection*{Others}
Some other side-channel targets also include spelling checking tools and font libraries~\cite{xu2015controlled}. The attack on font libraries is essentially the same as the attack on the graphic library GDK. By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information. Other side-channel attacks target the OS's kernel. One example is using the side-channel attack to break the kernel address space randomization (KASLR).
Many exploits rely on the knowledge of the memory location of a certain kernel function. Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time. Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal the mapping status of each page. After that, they detect kernel modules with unique size signatures to break KASLR. The second example relies on the side-channel vulnerabilities~\cite{cao2019principled} inside kernels to infer the TCP sequence numbers, which can be used by a third party to hijack connections between the client and the server~\cite{cao2016off}.

@@

\begin{itemize}
    \item Many tools can only analyze the source code or the intermediate representation level. However, side-channel are low-level problems in general.  Most existing tools are research prototypes. For some projects, the tools can only handle the benchmarks in their papers properly. 
    \item These tools heavily rely on SMT solvers. Despite SMT solvers having made incredible progress in performance, SMT solving is still the main bottleneck of these tools. SMT solvers are not good at non-linear arithmetic. However, such non-linear arithmetics are quite common in cryptography algorithms.  Recent studies show existing solvers still have bugs when dealing with real number calculations. These calculations are also common in media libraries and machine learning applications.
\end{itemize}

According to Table~\ref{table:side_channel_detection_tool}, some methods may choose to analyze the source code or the intermediate representations of the vulnerable software. However, it still cannot solve the problem. First, many widely-used libraries (e.g., Intel MKL) do not open the source code. Second, some libraries use hard-coded assembly code to pursue maximum performance.
Here, we introduce several tools. CacheAudit~\cite{182946} uses abstract domains to compute an
over-approximation of cache-based side-channel information leakage upper bound.
However, it is difficult to judge the sensitive level of the side-channel leakage based on the leakage provided by CacheAudit. Besides, CacheAudit is not scalable enough to analyze ciphers like RSA implementations. CacheS~\cite{236338} improves the approach from
CacheAudit with a new abstract model that only tracks
secret-related code. Like CacheAudit, CacheS cannot
indicate the sensitive level of side-channel vulnerabilities.
CaSym~\cite{Brotzman19Casym} introduces a static cache-aware symbolic reasoning technique to cover multiple paths in a target program. CaSym can work on two threat models: trace-based attacks and access-based attacks. Again, their
approaches cannot evaluate the sensitive level for each side-channel vulnerability, and it only works on small code snippets.

The dynamic approach, usually consisting of taint analysis and symbolic execution,
can perform a very precise analysis. CacheD~\cite{203878} takes a concrete execution trace and runs symbolic execution on the trace
to get a formula for each memory address. CacheD is
quite precise in avoiding false positives. However, CacheD is not able to detect secret-dependent control-flows. We adopted a similar approach to model the secret-dependent data accesses in the dissertation. \tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the trace when identifying secret-dependent data access vulnerabilities. \tool{} works on machine instructions directly instead of intermediate representations. Moreover, \tool{} finds secret-dependent control-flows at the same time and gives a precise quantification of the leakage. DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing and aligning different execution traces under various test inputs. After collecting execution traces, DATA aligns them and finds the differences. It uses statistical hypothesis testing to find true leakages. However, both imperfect trace alignment and a statistical testing result that DATA can produce false positives.
MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} adopts a similar approach from DATA by comparing all accessed addresses. It uses mutual information (MI) between sensitive input and execution state to quantify the information.

>>>>

\subsubsection*{Machine Learning Applications}
Recent side-channel attacks on machine learning applications mainly focus on recovering two types of sensitive information: the input of the model and the architecture of deep learning models. Hua et al.~\cite{hua2018reverse} were the first in the literature to reverse engineer the architecture of convolutional neural networks (CNNs) through the memory access patterns. Wei et al.~\cite{wei2018know} perform the side-channel attacks on an FPG-based convolution neural network by using the power consumption to recover inputs to the networks. For an image classification task trained by the MNIST dataset, their attacks can achieve up 89\% accuracy. CSI NN~\cite{batina2019csi} reverse engineered the multi-layer perception and convolution neural network based on the electromagnetic signals (EMs). Cache Telepathy~\cite{yan2020cache} introduces the cache-based side-channel attack to extract DNNs' architectures. We find that all existing approaches need a lot of domain knowledge and expertise to launch the attacks.

\subsubsection*{Media and Graphic Libraries}
Recent work also studies the side-channel attacks in media and graphic libraries. Gruss et at.~\cite{191010} show an attack that can infer keystrokes by exploiting secret-dependent memory accesses in the GDK library. In the controlled-channel attack~\cite{xu2015controlled}, Yuanzhong et al. demonstrate an attack to recover the outline of an image by exploiting the vulnerability in the inverse DCT function in libjpeg. Daimeng et al.~\cite{wang2019unveiling} present a cache attack on graphic libraries. Their approaches uses a machine learning approach to pick cache lines that can be exploitable to leak the most information.
\subsubsection*{Others}
Some other side-channel targets also include spelling checking tools and font libraries~\cite{xu2015controlled}. The attack on font libraries is essentially the same as the attack on the graphic library GDK. By exploiting the differences of memory accesses when the program renders different characters, an attacker can recover parts of the original sensitive information. Other side-channel attacks target the OS's kernel. One example is using the side-channel attack to break the kernel address space randomization (KASLR).
Many exploits rely on the knowledge of the memory location of a certain kernel function. Since Linux 4.12, the kernel loads core kernel image and device drivers at random positions during the boot time. Jang et al.~\cite{jang2016breaking} rely on side-channels to reveal the mapping status of each page. After that, they detect kernel modules with unique size signatures to break KASLR. The second example relies on the side-channel vulnerabilities~\cite{cao2019principled} inside kernels to infer the TCP sequence numbers, which can be used by a third party to hijack connections between the client and the server~\cite{cao2016off}.

@@

\begin{itemize}
    \item Many tools can only analyze the source code or the intermediate representation level. However, side-channel are low-level problems in general.  Most existing tools are research prototypes. For some projects, the tools can only handle the benchmarks in their papers properly. 
    \item These tools heavily rely on SMT solvers. Despite SMT solvers having made incredible progress in performance, SMT solving is still the main bottleneck of these tools. SMT solvers are not good at non-linear arithmetic. However, non-linear arithmetics are quite common in cryptography algorithms.  Recent studies show existing solvers still have bugs when dealing with real number calculations. These calculations are also common in media libraries and machine learning applications.
\end{itemize}

According to Table~\ref{table:side_channel_detection_tool}, some methods may choose to analyze the source code or the intermediate representations of the vulnerable software. However, it still cannot solve the problem. First, many widely-used libraries (e.g., Intel MKL) do not provide source code. Second, some libraries use hard-coded assembly code to pursue maximum performance.
CacheAudit~\cite{182946} uses abstract domains to compute an
over-approximation of cache-based side-channel information leakage upper bound.
However, it is difficult to judge the sensitive level of the side-channel leakage based on the leakage provided by CacheAudit. Besides, CacheAudit is not scalable enough to analyze ciphers like RSA implementations. CacheS~\cite{236338} improves the approach from
CacheAudit with a new abstract model that only tracks
secret-related code. Like CacheAudit, CacheS cannot
measure the amount of leaked information in each side-channel vulnerability.
CaSym~\cite{Brotzman19Casym} introduces a static cache-aware symbolic reasoning technique to cover multiple paths in a target program. CaSym can work on two threat models: trace-based attacks and access-based attacks. Again, their
approaches cannot evaluate the sensitive level for each side-channel vulnerability, and it only works on small code snippets.

The dynamic approach, usually consisting of taint analysis and symbolic execution,
can perform a very precise analysis. CacheD~\cite{203878} takes a concrete execution trace and runs symbolic execution on the trace
to get a formula for each memory address. CacheD is
quite precise in avoiding false positives. However, CacheD is not able to detect secret-dependent control-flows. We adopted a similar approach to model the secret-dependent data accesses in the dissertation. \tool{} differs from CacheD in that we do not use traditional taint tracking or domain knowledge to cut the execution trace when identifying secret-dependent data access vulnerabilities. \tool{} works on machine instructions directly instead of intermediate representations. Moreover, \tool{} finds secret-dependent control-flows at the same time and gives a precise quantification of the leakage. DATA~\cite{217537} detects address-based side-channel vulnerabilities by comparing and aligning different execution traces under various test inputs. After collecting execution traces, DATA aligns them and finds the differences. It uses statistical hypothesis testing to find true leakages. However, both imperfect trace alignment and the statistical testing that DATA uses can produce false positives.
MicroWalk~\cite{Wichelmann:2018:MFF:3274694.3274741} adopts a similar approach as DATA by comparing all accessed addresses. It uses mutual information (MI) between sensitive input and execution state to quantify the information.
